Visualizing Independence Using Extended Association and Mosaic Plots

### 2003-04-09 trunk/vcd/inst/doc/dsc2003-independence.Rnw
*** empty log message ***
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@249 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\SweaveOpts{engine=R,eps=FALSE}
\setkeys{Gin}{width=0.8\textwidth}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
grid.mosaicpairs(UCBAdmissions, type = "conditional", gp = gp.shading, main = NULL)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}

>>>>

\SweaveOpts{engine=R,eps=FALSE}
%\VignetteIndexEntry{Visualizing Independence Using Extended Association and Mosaic Plots}
%\VignetteDepends{vcd,MASS,grid}
%\VignetteKeywords{mosaic plot, association plot, independence, HCL colors}
%\VignettePackage{vcd}

\setkeys{Gin}{width=0.8\textwidth}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
##grid.mosaicpairs(UCBAdmissions, type = "conditional", main = NULL)
grid.mosaicpairs(UCBAdmissions, type = "conditional", permute = FALSE)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}
